\begin{Desc}
\item[Note:]This app requires a Google AJAX Search API Key. You can get one at \href{http://code.google.com/apis/ajaxsearch/signup.html.}{\tt http://code.google.com/apis/ajaxsearch/signup.html.} \end{Desc}
\begin{Desc}
\item[\hyperlink{todo__todo000001}{Todo}]Make this support everyhting Image\_\-Barcode supports:\begin{itemize}
\item Code 39\item Code 128\item EAN 13\begin{itemize}
\item {\bf Done!} \end{itemize}
\item INT 25\item PostNet\begin{itemize}
\item {\bf Will probably not be done, as it can not be read by most barcode scanners and has no practical purpose}\end{itemize}
\item UPCA\begin{itemize}
\item {\bf Done!} \end{itemize}
\end{itemize}


Support ISBN lookups with isbndb.com\end{Desc}
\begin{Desc}
\item[Author:]Dan Keenan - \href{http://dankeenan.org}{\tt http://dankeenan.org} \end{Desc}
\hypertarget{index_license}{}\section{License}\label{index_license}
Copyright (C) 2008 Dan Keenan

This program is free software: you can redistribute it and/or modify it under the terms of the GNU General Public License as published by the Free Software Foundation, either version 3 of the License, or (at your option) any later version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU General Public License for more details.

You should have received a copy of the GNU General Public License along with this program. If not, see $<$\href{http://www.gnu.org/licenses/}{\tt http://www.gnu.org/licenses/}$>$.



A \hyperlink{license}{full text } of this license is available 